Analysis: The Sound of Teaching Music 1

### 2019-10-21 script/RNotebook/dynamics.Rmd
correct typo
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Post-hoc (direct comparison)
```{r post-hoc3, echo = FALSE}
vel_acc_ttest_forte <- t.test(vel_acc_dyn$Mean[vel_acc_dyn$Condition == "performing" & vel_acc_dyn$Subcomponent == "FtoP"], vel_acc_dyn$Mean[vel_acc_dyn$Condition == "teaching" & vel_acc_dyn$Subcomponent == "FtoP"], paired = TRUE)
vel_acc_ttest_piano <- t.test(vel_acc_dyn$Mean[vel_acc_dyn$Condition == "performing" & vel_acc_dyn$Subcomponent == "PtoF"], vel_acc_dyn$Mean[vel_acc_dyn$Condition == "teaching" & vel_acc_dyn$Subcomponent == "PtoF"], paired = TRUE)
vel_acc_ttest_piano$p.value <- sprintf('%.6f', vel_acc_ttest_piano$p.value)

print(vel_acc_ttest_forte)
print(vel_acc_ttest_piano)
```

>>>>

### Post-hoc (direct comparison)
```{r post-hoc3, echo = FALSE}
vel_acc_ttest_ftop <- t.test(vel_acc_dyn$Mean[vel_acc_dyn$Condition == "performing" & vel_acc_dyn$Subcomponent == "FtoP"], vel_acc_dyn$Mean[vel_acc_dyn$Condition == "teaching" & vel_acc_dyn$Subcomponent == "FtoP"], paired = TRUE)
vel_acc_ttest_ptof <- t.test(vel_acc_dyn$Mean[vel_acc_dyn$Condition == "performing" & vel_acc_dyn$Subcomponent == "PtoF"], vel_acc_dyn$Mean[vel_acc_dyn$Condition == "teaching" & vel_acc_dyn$Subcomponent == "PtoF"], paired = TRUE)

print(vel_acc_ttest_ftop)
print(vel_acc_ttest_ptof)
```
